Hierarchical Phrase-Based Grammar Extraction in Joshua

### 2009-11-30 papers/mt_marathon10_SuffixArray/paper.tex
More suffix array paper
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1168 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

@@

\shorttitle{Short}
\shortauthor{L. Schwartz}

@@

>>>>

\author{firstname=Chris, surname=Callison-Burch,
       address={Johns Hopkins University, Baltimore}}

@@

\shorttitle{Grammar Extraction}
\shortauthor{L. Schwartz, C. Callison-Burch}

@@

\section{Algorithms}

\subsection{Caching}
Discuss caching procedure

\subsection{Query Intersection}
\label{query-intersection}
Discuss query intersect

\begin{figure}

Put algorithm here.

\caption{Query intersection algorithm implemented in Joshua. This algorithm is based on a corrected version (Lopez, p.c.) of query intersection {\protect \cite{Lopez2008}}, with minor modifications as noted in section \ref{query-intersection}}
\end{figure}
